Web Processing - Standardized GIS Analyses for Cable Route Planning

### 2023-03-22 presentations/20230324_seh_final.tex
renamed final presentation: corrected the date
added new slides and images + gif

% !TeX spellcheck = en_GB
\documentclass[usenames,dvipsnames,aspectratio=169]{beamer}
\usetheme{Szeged}
\usecolortheme{beaver}
\usepackage{tikz}
\usepackage{subfig}
\setbeamertemplate{navigation symbols}{}
\usepackage{xcolor}

\title{Web Processing - Standardized GIS Analyses for Cable Route Planning}
\author{Sebastian Heiden}
\institute{Harz University of Applied Sciences}
\date{December 02, 2022}
\begin{document}

@@

	\section{Web Processing Service (Concluded)}
	\begin{frame}{Web Processing Service (Concluded)}
		\begin{itemize}
		\item goals: 
		\begin{itemize}
			\item use wps as a simple, standardized way
			\item optimize search algorithm
		\end{itemize}
		\item current: 
		\begin{itemize}
			\item testing PyWPS\footnote{https://pywps.readthedocs.io/en/latest/index.html}
			\item cost path (open Dijkstra implementation - QGIS-plugin)\footnote{https://github.com/Gooong/LeastCostPath}
		\end{itemize}
	\end{itemize}
	\end{frame}

	\section{From Cost Raster to Least Cost Path}
	\begin{frame}{From Cost Raster to Least Cost Path}
		\begin{figure}
			\centering
			\subfloat[\centering Cost Raster.]{{\includegraphics[width=.30\linewidth]{images/maps/CostRasterExample_cut.png} }}%
			\enskip
			\subfloat[\centering Aggregated Cost Raster.]{{\includegraphics[width=.30\linewidth]{images/maps/AggregatedCosts_cut.png} \label{fig:aggregation}}}%
			\enskip
			\subfloat[\centering Least Cost Path.]{{\includegraphics[width=.30\linewidth]{images/maps/LeastCostPathExample_cut.png} }}%

@@

			\subfloat[\centering 50~m Resolution.]{{\includegraphics[width=.45\linewidth]{images/maps/LeastCostPath_50m_small.png} }}%
			\qquad
			\subfloat[\centering 5~m, Clipped.]{{\includegraphics[width=.45\linewidth]{images/maps/LeastCostPath_5m_false_clipped_small.png} }}%

@@

	\begin{frame}{Speed-Up: Down Sampling}
	\end{frame}

	\begin{frame}{Speed-Up:Super Position Medium Resolution}
	\end{frame}

	\begin{frame}{Speed-Up:Validation}
	\end{frame}
\end{document}

>>>>

% !TeX spellcheck = en_GB
\documentclass[usenames,dvipsnames,aspectratio=169]{beamer}
\usetheme{Szeged}
\usecolortheme{beaver}
\usepackage{multimedia}
\usepackage{tikz}
\usepackage{subfig}
\setbeamertemplate{navigation symbols}{}
\usepackage{xcolor}

\title{Web Processing - Standardized GIS Analyses for Cable Route Planning}
\author{Sebastian Heiden}
\institute{Harz University of Applied Sciences}
\date{March 24, 2023}
\begin{document}

@@

	\section{Web Processing Service (Concluded)}
	\begin{frame}{Web Processing Service (Concluded)}
	\centering
	\movie[externalviewer]{\includegraphics[width=0.75\textwidth]{images/wps.png}}{images/wps.gif}

	\section{From Cost Raster to Least Cost Path}
	\begin{frame}{Reminder: Sampling Resolution}
		\begin{figure}
		\centering
		\subfloat[\centering 10~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_10m_false.png} }}%
		\enskip
		\subfloat[\centering 25~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_25m_false.png} }}% 
		\enskip
		\subfloat[\centering 50~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_50m_false.png} }}%

		\caption{Maps of the cost raster for all~touched set to False for different resolutions.}
		\label{fig:CostAllTouchedFalse}
		\end{figure}
	\end{frame}

	\begin{frame}{Reminder: Sampling Resolution}
		\begin{figure}
		\begin{figure}
			\centering
			\subfloat[\centering 10~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_10m_true.png} }}%
			\enskip
			\subfloat[\centering 25~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_25m_true.png} }}% 
			\enskip
			\subfloat[\centering 50~m]{{\includegraphics[width=.30\linewidth]{images/maps/CostRaster_50m_true.png} }}%

			\caption{Maps of the cost raster for all~touched set to True for different resolutions.}
			\label{fig:CostAllTouchedTrue}
		\end{figure}
		\end{figure}
	\end{frame}

	\begin{frame}{From Cost Raster to Least Cost Path}
		\begin{figure}
			\centering
			\subfloat[\centering Cost Raster.]{{\includegraphics[width=.30\linewidth]{images/maps/CostRasterExample_cut.png} }}%
			\enskip
			\subfloat[\centering Aggregated Cost Raster.]{{\includegraphics[width=.30\linewidth]{images/maps/AggregatedCosts_cut.png} \label{fig:aggregation}}}%
			\enskip
			\subfloat[\centering Least Cost Path.]{{\includegraphics[width=.30\linewidth]{images/maps/LeastCostPathExample_cut.png} }}%

@@

			\subfloat[\centering 50~m.]{{\includegraphics[width=.45\linewidth]{images/maps/LeastCostPath_50m_small.png} }}%
			\qquad
			\subfloat[\centering 5~m, Clipped.]{{\includegraphics[width=.45\linewidth]{images/maps/LeastCostPath_5m_false_clipped_small.png} }}%

@@

	\begin{frame}{Speed-Up: Medium Resolution}
		\begin{minipage}[t]{0.48\textwidth}
		bi-linear down sampling
		\begin{itemize}
			\item 59.3~m average distance
			\item closer to path from all touched True

			\item independent from cost ratios
		\end{itemize}
		\end{minipage}
		\hfill	
		\begin{minipage}[t]{0.48\textwidth}
			weighted average cost raster
			\begin{itemize}
				\item best ration 4:1 False:True
				\item 40.1~m average distance
				\item closer to path from all touched True
				\item Optimum: depends on cost ratio
			\end{itemize}
		\end{minipage}
	\end{frame}

	\begin{frame}{Speed-Up:Validation}
		\begin{minipage}[t]{0.48\textwidth}
			clipping
			\begin{itemize}
				\item best path: 3 times
				\item Speed-Up: Unpredictable
			\end{itemize}
		\end{minipage}
		\hfill	
		\begin{minipage}[t]{0.48\textwidth}
			bi-linear down sampling
			\begin{itemize}
				\item distance worse, than from original medium resolution
				\item Speed-Up: square of resolution
			\end{itemize}
		\end{minipage}
	\end{frame}

	\begin{frame}{Conclussion AND Outlook}

	\begin{minipage}[t]{0.48\textwidth}
		Conclusion
		\begin{itemize}
			\item provide Least Cost Path with WPS
			\item studied algoritmic Speed-Up
			     \begin{itemize}
			     	\item clipping
			     	\item medium resolution
			     \end{itemize}
		\end{itemize}
	\end{minipage}
	\hfill	
	\begin{minipage}[t]{0.48\textwidth}
		Outlook
		\begin{itemize}
			\item non algorithmic Speed-Up
			\item set of possible paths
			\item stability: pertubation
		\end{itemize}
	\end{minipage}
	\end{frame}
\end{document}
